\documentclass[12pt]{article}

\usepackage{fullpage}
\usepackage{color}
\newcommand{\comment}[1]{{\color{blue} #1}}

\begin{document}
We thank the reviewer for their kind remarks and useful comments.  The
manuscript has been revised as follows.


\noindent
\comment{define the jump notation [[ ]] used in line 6 of section 2.}
\begin{itemize}
\item fixed
\end{itemize}

\noindent
\comment{state explicitly that $\gamma_j$ is the surface of the jth
vesicle in $\gamma$, the union of all vesicles.}
\begin{itemize}
\item fixed
\end{itemize}

\noindent
\comment{define $s_{y}$ in the integral in the first equation of p. 3.}
\begin{itemize}
\item fixed
\end{itemize}

\noindent
\comment{line 2 above equation (2): change sigma to $\sigma_{k}$.}
\begin{itemize}
\item fixed
\end{itemize}

\noindent
\comment{insert `updated' before `provisional' in step 4 of the SDC
iteration in section 3.}
\begin{itemize}
\item fixed
\end{itemize}

\noindent
\comment{should it say `A first-order approximation of (2)' [i.e. not
(3)] in the first line of section 3.1?}
\begin{itemize}
\item Equations (2) and (3) are equivalent.  We now mention that the
first-order approximation is of (3), and equivalentlyis of (3), and
equivalently of (2). 
\end{itemize}

\noindent
\comment{give a suitable book reference for the Runge phenomenon
alluded to on page 5.}
\begin{itemize}
\item We have added a reference to {\em Interpolation and
Approximation} by Philip J.~Davis.
\end{itemize}

\noindent
\comment{define `reduced area' (first line of section 4).}
\begin{itemize}
\item fixed
\end{itemize}

\noindent
\comment{In section 4.1 say how the N=96 points are distributed.}
\begin{itemize}
\item fixed
\end{itemize}

\noindent
\comment{p. 7, line 3> Suggest change `in excess of' to `better than'.}
\begin{itemize}
\item We agree with the reviewers's suggestion.  This has been changed.
\end{itemize}

\noindent
\comment{Table 1, 2: Insert `$m$' after `number' in the table captions.
Give the time units for CPU time.}
\begin{itemize}
\item fixed
\end{itemize}


\end{document}
