\documentclass[preprint, 10pt]{elsarticle}

%% labeling 
%%   equations \label{e:equation_name}
%%   sections  \label{s:section_name}
%%   tables    \label{t:table_name}
%%   figures   \label{f:figure_name}
%%   alagorithms \label{a:algorithm_name}
%%   Apendix \label{A:appendix_name}

%% bibtex names: all lower case
%%   one author: biros89, ghattas91, ghattas91a, ghattas91b, ghattas91c 
%%   up to three authors:  biros-ghattas-smith99
%%   more than three authors:  biros-e98
%%
%% for graphs and figures:
%%    tikz (best) or  one of the following: matlab, xfig, ggplot,
%%     see: http://www.texample.net/tikz/examples/

\input{preambles.tex}

\newif\ifTikz
\Tikztrue
%\Tikzfalse

%\usepgfplotslibrary{external}
%\tikzexternalize

\begin{document}

\title{Adaptive Time Stepping for Vesicle Suspensions}

\author[fsu]{Bryan Quaife}\ead{bquaife@fsu.edu}
\author[ut]{George Biros}\ead{gbiros@acm.org}

\address[fsu]{Department of Scientific Computing,\\
  Florida State University, Tallahassee, FL, 32306.}
\address[ut]{Institute of Computational Engineering and Sciences,\\
  The University of Texas at Austin, Austin, TX, 78712.}

\begin{abstract} 
We present an adaptive high-order accurate time-stepping numerical
scheme for the flow of vesicles suspended in Stokesian fluids. Our
scheme can be summarized as an approximate implicit spectral deferred
correction (SDC) method.  Applying a fully-implicit SDC scheme to
vesicle flows is prohibitively expensive.  For this reason we introduce
several approximations.  Our scheme is based on a semi-implicit
linearized low-order time stepping method.  (Our discretization is
spectrally accurate in space.)   We expect that the accuracy can be
arbitrary-order, but our examples suffer from order reduction which
limits the observed accuracy to third-order.  We also use invariant
properties of vesicle flows, constant area and boundary length in two
dimensions, to reduce the computational cost of error estimation for
adaptive time stepping. We present results in two dimensions for
single-vesicle flows, constricted geometry flows, converging flows, and
flows in a Couette apparatus. We experimentally demonstrate that the
proposed scheme enables automatic selection of the time step size and
high-order accuracy.
\end{abstract}

\begin{keyword}
  Vesicle suspensions \sep Adaptive time stepping \sep Spectral deferred
  correction \sep Particulate flows \sep Stokesian flows 
\end{keyword}

\maketitle

\section{Introduction\label{s:intro}}
\input introduction.tex

\section{Formulation\label{s:formulation}} 
\input formulation.tex

\section{Numerical Scheme\label{s:numerics}}
\input numerics.tex

\section{Adaptive Time Stepping\label{s:adaptive}}
\input adaptive.tex

\section{Results\label{s:results}} 
\input results.tex

\section{Conclusions\label{s:conclusions}} 
\input conclusions.tex

\section{Acknowledgments\label{s:acknowledgments}} 
\input acknowledgments.tex

\begin{appendices}

\section{Complete SDC Formulation \label{a:appendix1}}
\input appendixA.tex

\end{appendices}



\bibliographystyle{plainnat} 
\biboptions{sort&compress}
\bibliography{refs}
\end{document}
